---
title: "Options Analytics: Manage Symbols"
author: "Justin Townsend"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Manage Symbols

This document outlines the symbol (data) loading approach for the index instruments under analysis. This includes the underlying, as well as related, common listed derivatives.

```{r indices}
# List symbols




summary(cars) # List of indices and number of observations, perhaps a summary?
```




```{r orats.side_by_side}
opts.side_by_side.orats <- function(l, orats.extras = 0) {
  
  # Class should be a list
  if (!is.list(l)) {
    stop("Functions expects options expiries as a list. Confirm you are providing an object of list. :-)")
  }
  else {
    
    # Declare empty data frame
    opts_side_by_side = data.frame()
    
    for (opts in 1:length(l)) {
      
      # Expiry string to date
      expiry <- as.character(names(l[opts]))
      
      # Dynamic name for the expiry dataframe (list index based)
      side_by_side <- paste0("side_by_side_", opts, sep = "")
      
      if (orats.extras == 0) {
        
        # Extracting options data frames
        calls <- as.data.frame(l[[opts]]["call"])
        puts <- as.data.frame(l[[opts]]["put"])
        
        # Side by side: calls / puts join
        by <- dplyr::join_by(call.Ticker == put.Ticker, call.Strike == put.Strike)
        side_by_side <- dplyr::full_join(calls, puts, by)
        side_by_side$exp <- expiry
        
      } else {
        
        # Extracting options extra data frames
        calls <- as.data.frame(l[[opts]]["call_extra"])
        puts <- as.data.frame(l[[opts]]["put_extra"])
        
        # Side by side: calls / puts join
        by <- dplyr::join_by(call_extra.ticker == put_extra.ticker, call_extra.strike == put_extra.strike)
        side_by_side <- dplyr::full_join(calls, puts, by)
        side_by_side$exp <- expiry
        
      }
      
      # Append expiry to existing expiries
      opts_side_by_side <- dplyr::bind_rows(opts_side_by_side, side_by_side)
    }
    
    return(opts_side_by_side)
    
  }
}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
